\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Reference}  % Add "Reference" into the table of contents

\bibitem{ATLAS:Aad20121}The ATLAS Collaboration, {\it Observation of a new particle in the search for the Standard Model Higgs boson with the ATLAS detector at the LHC},  Phys. Lett. B B716 (2012) 1-29.
\bibitem{Chatrchyan:2012xdj}The CMS Collaboration, {\it Observation of a new boson at a mass of 125 GeV with the CMS experiment at the LHC}, Phys. Lett. B 716 (2012) 30.
\bibitem{ATLAS:2014aga}The ATLAS Collaboration, {\it Observation and measurement of Higgs boson decays to WW* with the ATLAS detector}, Phys. Rev. D 92, 012006 (2015).
\bibitem{LHCXsec}The LHC Higgs Cross Section Working Group, {\it Handbook of LHC Higgs Cross Sections: 3. Higgs Properties}, arXiv: 1307.1347.
\bibitem{PDGReview}M. Tanabashi et al. (Particle Data Group), {\it 2018 Review of Particle Physics}, Phys. Rev. D 98, 030001 (2018).
\bibitem{Detector}The ATLAS Collaboration, {\it The ATLAS Experiment at the CERN Large Hadron Collider}, JINST 3 (2008) S08003.
\bibitem{PID}Christian Lippmann, {\it Particle identification}, Nucl.Instrum.Meth. A666 (2012) 148-172.
\bibitem{ATLASComNote}Claudia Bertella et al., {\it Measurements of the Higgs boson production cross section via ggF and VBF in $H\rightarrow WW^{(*)} \rightarrow l\nu l\nu$ with 36.1 fb$^{−1}$ of data collected with the ATLAS detector at $\sqrt{s}$=13 TeV}, ATL-COM-PHYS-2017-1094.
\bibitem{HWWRun2Paper}The ATLAS Collaboration, {\it Measurements of gluon-gluon fusion and vector-boson fusion Higgs boson production cross-sections in the $\hwwlnln$ decay channel in pp collisions at $\com = $13 TeV with the ATLAS detector}, Phys. Lett. B 789 (2019) 508.

\end{thebibliography}
\newpage
